---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# firesale

<!-- badges: start -->
[![R-CMD-check](https://github.com/thomasp85/firesale/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomasp85/firesale/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/thomasp85/firesale/graph/badge.svg)](https://app.codecov.io/gh/thomasp85/firesale)
<!-- badges: end -->

firesale is a plugin for [fiery](http://fiery.data-imaginist.com/) that provides
a (potentially persistent) data store based on path parameters and client id.

It builds upon the [storr](https://richfitz.github.io/storr) package and thus
provides a multitude of storage backends to suit your need while providing the
same interface for your server logic.

## Installation

``` r
# You can install marquee from CRAN
pak::pak("firesale")

# Or get the development version from Github
pak::pak("thomasp85/firesale")
```

## Example
Using firesale is quite simple. You initialise the plugin and then attach it to
your fiery server:

```{r}
library(firesale)

ds <- FireSale$new(storr::driver_environment())

ds
```

Once created you attach it like any other plugin

```{r}
app <- fiery::Fire$new()

app$attach(ds)

app
```

Now, your request handlers will have access to a `datastore` element in their
`arg_list` argument which will grant you access to the datastore. The
`datastore` will itself contain two elements: `global` and `session`. The former
gives access to a datastore shared by all sessions, while the latter is scoped
to the session of the request being handled

```{r}
app$on("request", function(request, response, arg_list, ...) {
  response$status <- 200L

  # Use `session` to see if this is the first time
  if (!isFALSE(arg_list$datastore$session$first)) {
    # Store number of unique visitors in `global`
    arg_list$datastore$global$count <- (arg_list$datastore$global$count %||% 0) + 1

    response$body <- paste0(
      "This is your first visit\n",
      "You are visiter number ",
      arg_list$datastore$global$count
    )
    arg_list$datastore$session$first <- FALSE
  } else {
    response$body <- "You've been here before"
  }
})
```

As can be seen, the `datastore` and its element are list-like and you can treat
`session` and `global` pretty much how you would a normal list in terms of
getting and setting values.
